Calculating life expectancy and exploring missingness

### 2016-10-26 Code/1_Explore_Data_v2.Rmd

```{r load_libs, echo=F, warning=F, message=F}
library(plyr)
library(dplyr)
library(ggplot2)
library(tidyr)
source("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/life_expectancy_functions.R")
```

@@

ggplotly(ggplot(updated, aes(y = Ages, x = start)) + 
           geom_segment(aes(xend = finish, col = Cause.of.death, yend = Ages), lwd = 4) +
           xlab("Contribution to life expectancy gap") +
           ylab("Age group\n") + theme_minimal() +
           geom_vline(xintercept = 0))
```

>>>>

```{r load_libs, echo=F, warning=F, message=F}
library(plyr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(plotly)
source("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/life_expectancy_functions.R")
```

@@

ggplotly(ggplot(updated, aes(y = Ages, x = start)) + 
           geom_segment(aes(xend = finish, col = Cause.of.death, yend = Ages), lwd = 4) +
           xlab("Contribution to life expectancy gap") +
           ylab("Age group\n") + theme_minimal() +
           geom_vline(xintercept = 0))

#add total column for graphing purposes
total <- updated %>% ungroup() %>%
  group_by(Ages) %>%
  summarise(total = sum(C_xi))

total2 <- dplyr::bind_rows(first, total)
levels(total2$Cause.of.death) <- c(levels(total2$Cause.of.death), "All causes combined")
total2$Cause.of.death[is.na(total2$total)==F] <- "All causes combined"

#need to add a outlined segment for the ttoal group...
```
